---
title: "potential Transpiration from pot et and canopy leaf area index"
author: "ChenKozulin"
date: "29 בנובמבר 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

# the question the function is being used to answer

The function computes the expected canopy transpiration from data of potential evapotranspiration and canopy leaf area index.

# theory behind the function

Novák and Havrila (2005) note that the use of the PM model to assess transpiration is limited by the poor ability to calculate canopy resistance, which is influenced by a variety environmental parameters.
Instead, they propose to use a semi-emperical model developed by Novak (1995)
According to this model, potential transpiration (Etp)can be calculated 
as a function of potential evapotranspiration (Ep) and canopy leaf area index (ω0). 

Novák and Havrila (2005) Transpiration of Plants: A Review of Calculation Methods. Geophysical Research Abstracts, Vol. 7, 07181 SRef-ID: 1607-7962/gra/EGU05-A-07181

Novák (1995) Evapotranspiration and its estimation, Veda, Bratislava, 260 pp., (in Slovak)

```{r canopy transpiration from pot ET and canopy LAI}
#example application of your function with data 

# potential evapotranspiration (mm/day)

Ep=c(4.7,4.6,5.2,4.3,3.7,3.1)

# canopy leaf area index coefﬁcient. 
beta= c(0.45, 0.47,0.49,0.51,0.53,0.55)
# canopy leaf area index
omega0= c(0.5,0.75,1.4,1.47,1.5,1.6)



# Calculate potential transpiration (Etp)from potential evapotranspiration (Ep) and canopy leaf area index (omega0)
Etp=Ep*exp(1-exp(-beta*omega0))
```

## Including Plots


```{r Pot Et, echo=FALSE}
# summary of results
summary(Etp)
summary(Ep)
summary(beta)
summary(omega0)
plot(omega0,Etp,type="b")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
