---
title: "transpiration from yeild"
author: "ChenKozulin"
date: "28 בנובמבר 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

# the question the function is being used to answer

#'The function computes the expected canopy transpiration from biomass yeild.

# theory behind the function
#'According to: Novak, V., & Van Genuchten, M. T. (2008). Using the transpiration 
#'regime to estimate biomass production. Soil science, 173(6), 401-407.


#' 

```{r transpiration from yeild}
#example application of your function with data 

#dry biomass produced per unit area (t/ha)
Y<-c(0,2,4,6,8,10,12)

#crop water use efficiency (t/ha/cm)
kt=0.71

#intersection of the equation with the vertical axis
Y0=2.4

#Calculate transpiration from yeild
Et=(Y+Y0)/kt
```

## Including Plots



```{r transpiration, echo=FALSE}
# summary of results
summary(Y)
summary(Et)
plot(Et,Y)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
